\sysfull

### 2018-08-06 paper/asplos19/coalescing.tex
Coalescing section adapted

Different coalescing strategies adhere mainly to the template in Algorithm~\ref{algo:genCoalescing}, varying in only a few {\em characteristic operations} that the algorithm leaves deliberately abstract. A strategy's reboot update function, $f_\text{reboot}$, updates $B$, the target budget, after a reboot. A strategy's weight lookup function, $f_\text{weight}$, returns the a task's weight.  A strategy's commit update function, $f_\text{commit}$, updates $B$ after a successful commit. The following sections detail several possible coalescing strategies that we developed for \sys, albeit not the only possible. In fact, \sys \emph{allows programmers to design their own strategy} to implement and link to \sys’s task scheduler.

@@

A very simple {\em energy-oblivious} (EO) coalescing strategy treats all tasks as having unity weight and varies the size of a coalesced task linearly. In such a scheme, the number of tasks to coalesce, $B$, increases by a constant $x$ when a coalesced sequence of tasks commits, and decreases by the same constant $x$ when a coalesced sequence of tasks fails to complete, i.e., after a power failure. The characteristic operations of the energy-oblivious strategy are
%
\begin{equation}
	\begin{split}
		f_\text{reboot}(B) & = B - x, \\
		f_\text{weight}(T_\text{i}) & =  1, \\
		f_\text{commit}(B) & = B + x.
	\end{split}
\end{equation}
%
The energy-oblivious strategy reacts slowly to the variation in the energy required to execute different tasks and to the variation in the effective quantum of energy available to the device. With the successful commit of each coalesced task sequence, the coalescing target increases. Eventually, the target may be too high and a coalesced task composed of only fewer tasks will commit without interruption by a power failure. The strategy then linearly decreases the coalescing target, eventually reaching a coalescing target that allows completion. A key limitation of this algorithm lies in the equality of the target decrease in $f_\text{reboot}$ and the increase in $f_\text{commit}$. Let us assume $x=1$. If, after $k$ successful commits the target must decrease to its original value $B-k$ due to an energy drop, this strategy requires $k$ successive power failures.

@@

The \emph{Energy-Guided} (EG) coalescing strategy adapts its coalescing target more quickly, addressing a key limitation of the EO, to adhere to changes in energy conditions. It uses its recent execution history as  mean to measure energy availability and alters its target accordingly. By relying on the history of execution EG eliminates the problem of frequent power failures a single coalesced task. In fact EG can reduce its target to one from any coalesced target in at most two successive power failures. For instance, if the execution is interrupted after finishing a single task the history will be one ($H = 1$) and the target will be set to one also. While a history of $H$ suggests that there is sufficient energy to coalesce and successfully commit $H$ tasks (i.e., to set $B = H$). EG conservatively sets $B$ equal to half of $H$ moderating the risk of a very long coalesced task. We experimented with a range of fraction values, settling on one half as the default for EG, because one half had the highest performance. The EG algorithm is characterized by the following functions
%
\begin{equation}
	\begin{split}
		 f_\text{reboot}(H) & = \lceil(H / 2)\rceil,\\
		 f_\text{weight}(T_\text{i}) & = 1, \\
		 f_\text{commit}(B) & = \lceil(B / 2)\rceil.
	\end{split}
\end{equation}
%
Fig.~\ref{fig:hg-coal} illustrates the operation of the EG. The figure shows two power cycles following the $i$th, the latter having an
execution history $H^{(i)} = 4$. Based on that, $B$ is initially set to two and then decreases to one. Once the value of $B$ reaches one, EG is, in effect, expecting a power failure, justifying the conservative approach. After the power failure, EG uses the most recent history $H^{(i+1)} = 8$ to set $B = 4$ and continue execution.

@@

Instead, WEG associates a non-unity weight with each task in the program. WEG tracks the sum of the weights of tasks in a coalesced sequence of tasks. When the sum of weights reaches $B$, the target, WEG commits the coalesced task. WEG differs from EO and HG by explicitly accounting for the variation in energy cost of a program's tasks, eliminating the assumption that all tasks do the same work, which is a key limitation. WEG has the same characteristic operations as HG, except that $f_\text{weight}(T_\text{i}) = W_\text{i}$.

The effectiveness of the WEG algorithm hinges on correctly identifying the weight of each task, which WEG assumes is {\em statically} available. Profiling the time and energy cost of tasks in a program is a difficult, orthogonal problem~\cite{cleancut_2018,baghsorkhi_cgo_2018}. WEG could use the result of an arbitrarily sophisticated profiling procedure. To produce a concrete result in this paper, we give WEG access to a simple profile of task run time collected offline using a single fixed input. WEG stores the profile in a lookup table that maps a task's identifier to its weight, making the information available to \sys's scheduler at run time.

>>>>

Different coalescing strategies adhere mainly to the template in Algorithm~\ref{algo:genCoalescing}, varying in only a few {\em characteristic operations} that the algorithm leaves deliberately abstract. A strategy's reboot update function, $f_\text{reboot}$, updates $B$, the target budget, after a reboot. A strategy's weight lookup function, $f_\text{weight}$, returns the a task's weight.  A strategy's commit update function, $f_\text{commit}$, updates $B$ after a successful commit. The following sections detail several possible coalescing strategies that we developed for \sys, albeit not the only possible. In fact, \sys \emph{allows programmers to design their own strategy} to implement and link to \sys's task scheduler.

@@

A very simple {\em energy-oblivious} (EO) coalescing strategy treats all tasks as having unity weight and varies the size of a coalesced task linearly. In such a scheme, the number of tasks to coalesce, $B$, increases by a constant $x$ when a coalesced sequence of tasks commits, and decreases by the same constant $x$ when a coalesced sequence of tasks fails to complete, i.e., after a power failure. The characteristic operations of the energy-oblivious strategy are
%
\begin{equation}
	\begin{split}
		f_\text{reboot}(B) & = B - x, \\
		f_\text{weight}(T_\text{i}) & =  1, \\
		f_\text{commit}(B) & = B + x.
	\end{split}
	\label{eq:eo}
\end{equation}
%
The energy-oblivious strategy reacts slowly to the variation in the energy required to execute different tasks and to the variation in the effective quantum of energy available to the device. With the successful commit of each coalesced task sequence, the coalescing target increases. Eventually, the target may be too high and a coalesced task composed of only fewer tasks will commit without interruption by a power failure. The strategy then linearly decreases the coalescing target, eventually reaching a coalescing target that allows completion. A key limitation of this algorithm lies in the equality of the target decrease in $f_\text{reboot}$ and the increase in $f_\text{commit}$. Let us assume $x=1$. If, after $k$ successful commits the target must decrease to its original value $B-k$ due to an energy drop, this strategy requires $k$ successive power failures.

@@

The \emph{Energy-Guided} (EG) coalescing strategy adapts its coalescing target more quickly, addressing a key limitation of the EO, to adhere to changes in energy conditions. It uses its recent execution history as  mean to measure energy availability and alters its target accordingly. By relying on the history of execution EG eliminates the problem of frequent power failures a single coalesced task. In fact EG can reduce its target to one from any coalesced target in at most two successive power failures. For instance, if the execution is interrupted after finishing a single task the history will be one ($H = 1$) and the target will be set to one also. While a history of $H$ suggests that there is sufficient energy to coalesce and successfully commit $H$ tasks (i.e., to set $B = H$). EG conservatively sets $B$ equal to half of $H$ moderating the risk of a very long coalesced task. We experimented with a range of fraction values, settling on one half as the default for EG, because one half had the highest performance. The EG algorithm is characterized by the following functions
%
\begin{equation}
	\begin{split}
		 f_\text{reboot}(H) & = \lceil(H / 2)\rceil,\\
		 f_\text{weight}(T_\text{i}) & = 1, \\
		 f_\text{commit}(B) & = \lceil(B / 2)\rceil.
	\end{split}
	\label{eq:eg}
\end{equation}
%
Fig.~\ref{fig:hg-coal} illustrates the operation of the EG. The figure shows two power cycles following the $i$th, the latter having an
execution history $H^{(i)} = 4$. Based on that, $B$ is initially set to two and then decreases to one. Once the value of $B$ reaches one, EG is, in effect, expecting a power failure, justifying the conservative approach. After the power failure, EG uses the most recent history $H^{(i+1)} = 8$ to set $B = 4$ and continue execution.

@@

Instead, WEG associates a non-unity weight with each task in the program. WEG tracks the sum of the weights of tasks in a coalesced sequence of tasks. When the sum of weights reaches $B$, the target, WEG commits the coalesced task. WEG differs from EO and HG by explicitly accounting for the variation in energy cost of a program's tasks, eliminating the assumption that all tasks do the same work, which is a key limitation. WEG is characterized the same way as HG (equation (\ref{eq:eg})), except that $f_\text{weight}(T_\text{i}) = W_\text{i}$.

The effectiveness of the WEG hinges on correctly identifying the weight of each task, which WEG assumes is {\em statically} available. Profiling the time and energy cost of tasks in a program is a difficult, orthogonal problem~\cite{cleancut_2018,baghsorkhi_cgo_2018}. WEG could use the result of an arbitrarily sophisticated profiling procedure. To produce a concrete result in this paper, we give WEG access to a simple profile of task run time collected offline using a single fixed input. WEG stores the profile in a lookup table that maps a task's identifier to its weight, making the information available to \sys's scheduler at run time.
